\LARGE \bf A Pipeline to Assemble (Near-)Collision Footage Datasets

### 2021-03-24 paper.tex
Fixing figure title actor
Few fixes from peer activity.

Users may define their own search terms to be used when querying the video repository. This value can be set in a YAML pipeline configuration file. By default, our scrapers query using the keywords: \texttt{Car crash dashcam}. Currently we support querying Reddit and YouTube, downloading from YouTube and Imgur. Users that want to pull from a video repository that is not currently implemented should create a custom executor and implement the \texttt{iCrawler} interface. This new executor should be added as an entry point in a new YAML configuration and should generate and return a \texttt{MetaDataItem} with video source information to be used by a subsequent and corresponding downloader. \texttt{MetaDataItem} objects are fed into the \texttt{UniversalDownloader} which aggregates \texttt{iDownloader} implementations and distributes \texttt{MetaDataItem} objects to their corresponding downloader via regular expressions matching of source URL's. New downloaders should be registered with the \texttt{UniversalDownloader} via a YAML pipeline configuration along with a regular expression string for URL matching.

@@

\begin{figure}
  \begin{lstlisting}[language=json]
    {
      "collision_type":"",
      "description":"",
      "download_src":"",
      "tags": {
        "reddit_post_info":{
          "id":"<post_id>"
          "title":"title"
        }
      },
      "title":"Title of the Video",
      "url":"http:/www.myvideo.com",
      "is_split_url": false,
      "enum_tags": ["CollisionWithRecordingVehicle"],
      "start_i": 0,
      "end_i": 60,
      "collision_locations": [],
      "bb_fields": {
        "clss": [],
        "frames": [],
        "has_collision": [],
        "ids": [],
        "x1s": [],
        "y1s": [],
        "x2s": [],
        "y2s": [],
      }
    }
  \end{lstlisting}
    \caption{Example Metadata Produced by the Pipeline}
    \label{metadata_example}
\end{figure}

@@

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by participant},
      xlabel={Number of participants},
      ylabel={Frequency (\# of videos)},
      xtick=data,
      xticklabels from table={\byactors}{X}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byactors;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos by number of actors}
		\label{fig:vids-by-actors}
\end{figure}

>>>>

Users may define their own search terms to be used when querying the video repository. This value can be set in a YAML pipeline configuration file. By default, our scrapers query using the keywords: \texttt{Car crash dashcam}. Currently we support crawling Reddit and YouTube to locate videos that are of interest, and downloading videos hosted on YouTube and Imgur. Users that want to pull from a video repository that is not currently implemented should create a custom executor and implement the \texttt{iCrawler} interface. This new executor should be added as an entry point in a new YAML configuration and should generate and return a \texttt{MetaDataItem} with video source information to be used by a subsequent and corresponding downloader. \texttt{MetaDataItem} objects are fed into the \texttt{UniversalDownloader} which aggregates \texttt{iDownloader} implementations and distributes \texttt{MetaDataItem} objects to their corresponding downloader via regular expressions matching of source URL's. New downloaders should be registered with the \texttt{UniversalDownloader} via a YAML pipeline configuration along with a regular expression string for URL matching.

@@

\begin{figure}
  \begin{lstlisting}[language=json]
    {
      "collision_type":"",
      "description":"",
      "download_src":"",
      "tags": {
        "reddit_post_info":{
          "id":"<post_id>"
          "title":"title"
        }
      },
      "title":"Title of the Video",
      "url":"http://www.myvideo.com",
      "is_split_url": false,
      "enum_tags": ["CollisionWithRecordingVehicle"],
      "start_i": 0,
      "end_i": 60,
      "collision_locations": [],
      "bb_fields": {
        "clss": [],
        "frames": [],
        "has_collision": [],
        "ids": [],
        "x1s": [],
        "y1s": [],
        "x2s": [],
        "y2s": [],
      }
    }
  \end{lstlisting}
    \caption{Example Metadata Produced by the Pipeline}
    \label{metadata_example}
\end{figure}

@@

\begin{figure}[htpb]
		\centering
    \begin{tikzpicture}
    \begin{axis}[
      title={Videos by participant},
      xlabel={Number of participants},
      ylabel={Frequency (\# of videos)},
      xtick=data,
      xticklabels from table={\byactors}{X}
    ]
    \addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byactors;
    \end{axis}
    \end{tikzpicture}
		\caption{Videos by number of participants}
		\label{fig:vids-by-participant}
\end{figure}
